An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-02 poly-embed-journal/poly-embed-journal.tex
tweaks in sec 2,3

\begin{definition}
  \raf{Trying this out:}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
\end{definition}

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  \raft{Alternative: define ``embed over $S$'' first, and then ``embed'' means over some representative $S$.  Let's see if that would work.  Then we can call out $S$ to specify it if we want, but we don't need to carry it around everywhere and change all the statements if we don't want to call out $S$.}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$ and the risks are polyhedral.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{I'm going ahead with the proposed definition regarding $S$, since I think we can't avoid that for this result at least.}
  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ over $\Sc\subseteq \R$ via the embedding $\varphi:S\to\reals^d$.
  Since $\Sc$ is representative, for all $p\in\simplex$ we have $\Sc \cap \gamma(p) \neq \emptyset$.
  \raf{Can we remove $\gamma'$ and show more directly that $\U$ is representative for $\Gamma$?  We only use the second part of Lemma~\ref{lem:loss-restrict} anyway.}
  Take $\U := \varphi(\Sc)$, and consider $\Sc$ is representative of $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
  Therefore, we have $\U$ representative of $L|_\U$ since $\Gamma(p)$ is nonempty, and $\U$ is representative of $L$.
%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Moreover, the risks are polyhedral as $\risk{\ell}$ is the pointwise max of a finite set of linear functions.

>>>>

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is \emph{minimally representative} or a \emph{minimal representative set} if it has the smallest cardinality among all representative sets.
\end{definition}

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\raf{We should probably add the type of $\ell$ and $L$ in each lemma/prop/thm statement, or add something like: ``throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^Y$ and $L:\reals^d\to\reals^\Y$''.}

\begin{proposition}\label{prop:embed-bayes-risks}
  Let discrete loss $\ell$ be given.
  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{I'm going ahead with the proposed definition regarding $S$, since I think we can't avoid that for this result at least.}
  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:S\to\reals^d$.
  Since $\Sc$ is representative, for all $p\in\simplex$ we have $\Sc \cap \gamma(p) \neq \emptyset$.
  \raf{Can we remove $\gamma'$ and show more directly that $\U$ is representative for $\Gamma$?  We only use the second part of Lemma~\ref{lem:loss-restrict} anyway.}
  Take $\U := \varphi(\Sc)$, and consider $\Sc$ is representative of $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
  Therefore, we have $\U$ representative of $L|_\U$ since $\Gamma(p)$ is nonempty, and $\U$ is representative of $L$.
%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Moreover, the risks are polyhedral as $\risk{\ell}$ is the pointwise max of a finite set of linear functions.
